%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% \usepackage[T1]{fontenc}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Large{Jason Hoch}} \\
    \vspace{2pt}
    \small{jrshoch@gmail.com \vline\hspace{0.25pt} +1\hspace{-2pt} (203)\hspace{-2pt} 482-0837}
\end{center}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Massachusetts Institute of Technology}{Boston, MA}
      {Bachelor of Science, Computer Science, Theoretical Math;  GPA: 4.8/5.0}{Aug 2009 -- Jun 2013}
      \resumeItemListStart
        \resumeItem{Favorite classes}{Compilers, Computability Theory, Algebraic Combinatorics}
        \resumeItem{Honors}{Putnam Honorable Mention, Battlecode Finalist}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Bento}{San Francisco, GA}
      {Co-founder}{Mar 2020 - Sept 2020}
      \resumeItemListStart
        \resumeItem{Cross-functional coordination}
          {Built a product that listened to Slack channels and pulled in shared GSuite, Github, Jira, Figma links. Presented users with digest of teammates' activities across tools by utilizing APIs}
        \resumeItem{YC Summer 2020}
          {Managed 1-2 engineering contractors, reached 15 weekly active users, raised \$100k+ pre-seed capital, integrated with 8 SaaS applications.  Synced 1000s of resources across those applications with low latency}
      \resumeItemListEnd

    \resumeSubheading
      {Newfront Insurance}{San Francisco}
      {Senior Software Engineer, Engineering Manager}{Sept 2018 - Mar 2020}
      \resumeItemListStart
        \resumeItem{Hiring}
          {Was a key decision-maker in leveling up the engineering team from 5 to 25 over 13 months}
        \resumeItem{Mentorship}
          {Provided mentorship to intern, junior, and senior engineers}
        \resumeItem{Engineering Practices}
          {Introduced Typescript, seeing the codebase go from 0\% to 90\% static types over 15 months.  Introduced CI/CD tooling, measurement, and practices.  Introduced and oversaw code review practices during the critical transition from 5 to 15 engineers.  Introduced and oversaw all logging and telemetry}
        \resumeItem{Infrastructure}
          {Reworked a the stateful monolithic backend to allow for high availability; audited and overhauled API for security vulnerabilities; managed introduction of GraphQL, balancing desires of engineers against those of the VP of Engineering}
        \resumeItem{DevOps}
          {Led an effort to reduce build times from 20 to 3 minutes. Managed a project to convert our deployment process from Heroku clone-and-build to Docker images. Transitioned the team from scrolling through logs to searching across millions of logs per day, measuring API latency, and distributed tracing capabilities}
        \resumeItem{Support}
          {Was the go-to engineer for the most critical production issues on a team of 25}
      \resumeItemListEnd

    \resumeSubheading
      {Palantir}{Palo Alto; Paris; New York}
      {Engineering Lead, Forward Deployed Engineer, Software Developer}{Jul 2013 - Aug 2018}
      \resumeItemListStart
        \resumeItem{Hiring}
          {Interviewed 100s of engineers.  Met with all engineers receiving an offer in NY for sell conversations}
        \resumeItem{Mentorship}
          {Mentored 4 interns in my first 2 years at the company}
        \resumeItem{ETL product suite, Engineering lead}
          {Led a team of 20 engineers across 3 time zones that managed 25 microservices deployed at dozens of Palantir customers.  Product capabilities included unit testing and CI of ETL transforms, ETL transform code VCS server, coordination of Spark jobs, ETL transform pull request and code reviews, and writing and running ETL transforms in multiple open and propietary languages}
        \resumeItem{ETL administration, Insurance customer}
          {Administered a Palantir stack used by 40 data scientists and data engineers.  ETL pipeline included 2500 tranforms.  Provided guidance to nascent product for map-like pipeline exploration.  Helped transition stack from Foundry 0.x to 1.x}
        \resumeItem{Aggregations API}
          {Developed and implemented an Elasticsearch-like JSON HTTP API for propietary MapReduce-like service.  API was consumed by 100+ engineers across the company and at dozens of Palantir customers.  Built first bridge between Foundry and Gotham products}
        \resumeItem{Federated Data Import}
          {Implemented 10x scale and speed improvement of federated data imports into Palantir Gotham}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Skills and Interests}
  \resumeSubHeadingListStart
    \resumeSubItem{Technologies}
      {NodeJS, React, Gradle, Docker, yarn/npm, CircleCI, Datadog, Postgres, GraphQL, Terraform, k8s, Spark, Jackson, Dropwizard, Protocol Buffers, IntelliJ, Visual Studio Code, Eclipse, Github, Heroku, tmux, Vercel, LogDNA, Atlantis}
    \resumeSubItem{Languages}
      {Java, 5+ years; Typescript, 2+ years; SQL, Golang, Bash, Python}
    \resumeSubItem{Interests}
      {Math, Chess, History, Running, Markets, Cooking, Politics}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
